% !TeX root = ..\academicWriting.tex SHOULD WORK BUT DOESN'T :(

\begin{frame}{What's LaTeX?}
 \begin{fullpageitemize}
  \itemR Markup language
  \itemR High quality documents
  \itemR Consistent output every time
  \itemR Separation of style from text
  \itemR Easy academic format: equations, glossaries, bibliography, table of contents, cross references\ldots
 \end{fullpageitemize}
 \note{LaTeX is a markup language aiming to produce high quality documents. It was created by academics, with the idea of having consistent output every time (forget that table that moved itself from page 2 to 5), separation of style from text (that has two objetives: helps centre oneself in the content and allows the reuse of material) and easy academic format (equations are not a pain, glossaries, bibliographies and tables of contents automatic and cross referencing trivial)
 
So let's see how can we start using the stuff. As a note I'll talk mostly about free software because that's what I use}
\end{frame}

\begin{frame}{What do I need?}
 \null{\color{colororange}\largetext{Option 1}}
 \begin{itemize}
  \item \textbf{Editor}: general purpose or specific (\href{http://www.xm1math.net/texmaker/}{Texmaker}, \href{https://www.tug.org/texworks/}{TeXworks}, \href{https://kile.sourceforge.io/}{Kile})
  
  \item \textbf{Distribution}: \href{https://miktex.org/}{MikTeX} (Windows), \href{https://tug.org/texlive/}{TeXLive} (cross-platform) $\rightarrow$ compiler + packages
 \end{itemize}
 \vspace{1ex}
 {\color{colororange}\largetext{Option 2}}
  \begin{itemize}
  \item \textbf{Online editor}: \href{https://www.overleaf.com/}{Overleaf}
 \end{itemize}
 
 \note{We're going to write in plain text so any editor can do. I use Emacs (in general I write in Org mode and export to LaTeX). Also the AucTeX mode is specially useful. For starters, and with the idea of not getting crazy, one can use a specific editor as Texmaker that I used to produce these slides.
 
 We also need a distribution of LaTeX. If you're on Windows I'd recommend MikTeX as it takes care of needed packages on its own.}
\end{frame}

\begin{frame}{The markup language}
- Packages, preamble, environments and commands
- Equations, tables, titles, figures 
\end{frame}

\begin{frame}{Structure of a document}

\end{frame}

\begin{frame}{Useful packages}

\end{frame}

\begin{frame}{Crossreferences}

\note{ref, paquete cleveref (cref, Cref), nameref}
\end{frame}

\begin{frame}{Bibliography}
 \begin{fullpageitemize}
  \itemR Bibliography stored in a {\inconsolatafont .bib} file 
  \itemR Managed by external program (\href{http://www.bibtex.org/}{BibTeX}, \ldots) 
  \itemR Additional compilation step: {\inconsolatafont latex - bibtex - latex - latex}
  \itemR Bibliography managers: JabRef, Zotero, \href{https://bibdesk.sourceforge.io/}{BibDesk} \ldots
 \end{fullpageitemize}
 
 \note{zotero-better-bibtex,  for Mac. 
 BibTeX comes with the standard LaTeX distribution, there are more options like Natbib, BibLaTeX}
\end{frame}

\begin{frame}[fragile]{Bibliography}

MWE with bibliography defined in {\inconsolatafont references.bib}:

\begin{lstlisting}[language={[LaTeX]TeX},texcsstyle=*\color{colororange}]
\documentclass[11pt]{article}
  \begin{document}
  
  As said in \cite{Knuth1997}...
    
  % Definition of bibliography
  \bibliography{references} % Path
  \bibliographystyle{plain} % Style
\end{document}
\end{lstlisting}

\note{Minimum working example}

\end{frame}

\begin{frame}[fragile]{Bibliography}

Where {\inconsolatafont references.bib} looks like:

\begin{lstlisting}[breaklines=false]
@book{Knuth1997,
  title={The art of computer programming},
  author={Knuth, Donald Ervin},
  volume={3},
  year={1997},
  publisher={Pearson Education}}
\end{lstlisting}
\note{A little trick is changing Scholar settings so that one can directly import to BibTex}
\end{frame}

\begin{frame}{Tools \& tricks}
 \begin{fullpageitemize}
  \itemR \href{https://www.overleaf.com/}{\textbf{Overleaf}}: templates and online editor
  \itemR \href{http://wiki.inkscape.org/wiki/index.php/LaTeX}{\textbf{Inkscape}}: image text as document text, LaTeX equation in images
  \itemR \href{https://www.ctan.org/tex-archive/support/excel2latex/}{\textbf{Excel2LaTeX}}: export tables with LaTeX format
  \itemR \href{http://detexify.kirelabs.org/classify.html}{\textbf{Detexify}}: find symbols
  \itemR \href{http://pandoc.org/}{\textbf{Pandoc}}: convert to \emph{any} format
  \itemR LyX
\end{fullpageitemize}
 
\note{\href{http://mathb.in}{MathB.in} 

\href{https://mathpix.com/}{Mathpix}: screenshot to equation} 
\end{frame}

\begin{frame}{References}
 \begin{fullpageitemize}
	\itemR\href{https://ondiz.github.io/cursoLatex/}{\emph{Curso no convencional de LaTeX}}. Ondiz Zarraga

	\itemR \href{http://www.khirevich.com/latex/}{\emph{Tips on Writing a Thesis in LaTeX}}. Siarhei Khirevich
 \end{fullpageitemize}
\end{frame}

\framecard[colorgreen]{
{\color{white}\hugetext{Let's go!}}
% xkcd
}